---
title: "Stat 343: Monte Carlo Integration"
output:
  pdf_document
---

\newcommand{\simiid}{{\mathrel {\mathop {\sim}\limits _{}^{\rm iid}}\,}}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(dplyr)
library(ggplot2)
```

It can be shown that if $\mu | x_1, \ldots, x_{15} \sim \text{Normal}(45.53, 1.953^2)$ and $X | \mu \sim \text{Normal}(\mu, 8^2)$, then $X | x_1, \ldots, x_{15} \sim \text{Normal}(45.53, 1.953^2 + 8^2)$

#### (1) Draw a sample of size 10^6 from a normal distribution with mean 45.53 and standard deviation $\sqrt{1.953^2 + 8^2}$; save your results in a variable called $x$.

```{r}
x <- rnorm(10^6, mean = 45.53, sd = sqrt(1.953^2 + 8^2))
```

#### (2) Use your sampled values $x$ to estimate the expected value of $W | x_1, \ldots, x_{15}$.

```{r}
mean(0.088 * x^3.069)
```

#### (3) Use your sampled values $x$ to estimate the posterior probability that a newly sampled fish of this species in California will have a weight $W$ between 25 and 30 pounds.

```{r}
mean((0.088 * x^3.069 >= 25) & (0.088 * x^3.069 <= 30))
```



